%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Yuvraj Sehgal}\\
    \small 437-335-5700 $|$ \href{mailto:ys19rk@brocku.ca4}{\underline{ys19rk@brocku.ca}} $|$ \href{https://ca.linkedin.com/in/yuvraj-sehgal}{\underline{linkedin.com/in/yuvraj-sehgal}} $|$ \href{https://github.com/17YuvrajSehgal}{\underline{github.com/17YuvrajSehgal}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Honours Bachelor of Science, Computer Science}{January 2021 -- Present}
    {Brock University, St. Catharines, ON}{}
    \resumeItemListStart
      \resumeItem{Expected Graduation:}{January 2025}
      \resumeItem{GPA:}{3.9/4.0}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%----------- TechSkill -----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Java, Python, C++, C} \\
    \textbf{Web Development}{: Java Spring, Java Spring boot, ReactJS, Angular, JSP, Java Servlets, HTML/CSS, JavaScript, Rest APIs, TypeScript} \\
    \textbf{Database Management}{: MySQL, OracleDB, PostgreSQL, MongoDB} \\
    \textbf{Build Tools}{: Maven, Gradle, Docker} \\
    \textbf{Testing and Automation Tools}{: Selenium, Appium, Gherkins, Cucumber, Web Driver, JUnit, Karma} \\
    \textbf{Other}{: Git, Github, JIRA, Confluence, Bitbucket, Bash, Word, Outlook, Excel, PowerPoint, SDLC} \\

    }}
 \end{itemize}
 \begin{center}

%-----------Experience-----------
\section{Experience}

 \resumeSubHeadingListStart
    \resumeSubheading
    {Full Stack Developer  }{July 2024 -- Present}
    {Mengalo}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Developed a full-stack chatbot using Spring Boot, LangChain, OpenAI, and React to provide real-time analytical insights, boosting product value and increasing customer acquisition. }
        \resumeItem{Integrated Power BI dashboard with React libraries, enhancing user experience and improving analytics visualization.}
        \resumeItem{Resolved six security vulnerabilities, protecting sensitive company and customer data and mitigating potential threats.}
        \resumeItem{Implemented code reviews, secure coding, Git management, and agile practices, boosting productivity and enhancing code quality in the startup.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
    {Research Assistant}{January 2024 -- Present}
    {Brock University}{St. Catharines, ON}
      \resumeItemListStart
        \resumeItem{Conducted empirical research with Professor Naser Ezzati-Jivan to evaluate the efficiency of generative AI in creating GitHub README files.}
        \resumeItem {Developed an automated README generator for GitHub repositories using Java Spring Boot, LangChain, and OpenAI models.}
        \resumeItem{Awarded the Match of Minds Scholarship for outstanding academic performance and research potential, selected as the sole recipient in the department based on faculty recommendations.}
        \resumeItem{Evaluated model performance on accuracy, completeness, and readability, offering insights into its effectiveness in automating project documentation.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
    {Automation Engineer Coop}{May 2024 -- August 2024}
    {Scotiabank}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Acquired Android automation skills and implemented automation for 20 test case scenarios using Java, Selenium, and Appium, reducing testing time by over 75\% within four months.}
        \resumeItem{Collaborated with the business quality assurance team to design test case scenarios that aligned with requirements and ensured business needs were met.}
        \resumeItem{Created comprehensive reports for automation results, collaborating with the business quality assurance team to ensure tests met requirements and aligned with BQA standards.}
        \resumeItem{Volunteered for tree planting in Toronto's Sun Valley.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\newpage
  \resumeSubHeadingListStart
    \resumeSubheading
    {Full Stack Developer Coop}{May 2023 -- August 2023}
    {Scotiabank}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Integrated SSL encryption in front-end and back-end code for the bank's Trade Floor Limit Management System (LMS), enhancing web application security.}
        \resumeItem{Developed comprehensive unit test cases using Java JUnit and Karma for the LMS website, increasing test coverage by 15\% and ensuring compliance with the bank’s 85\% minimum coverage mandate.}
      \resumeItem{Resolved cross-functional issues by collaborating with another department, enhancing efficiency and expanding the functionality of a Python script used for trade floor risk management.}
      \resumeItem{Identified a gap and created an extensive Confluence page to provide initial setup guidance, expediting onboarding for new team members and streamlining their integration process.}
      \resumeItem{Volunteered for tree planting in Toronto’s Don Valley during Community Day.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Experience 2 -----------
\resumeSubHeadingListStart
  \resumeSubheading
    {Automation Engineer Coop}{September 2022 -- December 2022}
    {Scotiabank}{Toronto, ON}
    \resumeItemListStart
      \resumeItem{Mastered automation techniques for quality assurance, crafting and implementing over 35 test scenarios within four month.}
      \resumeItem{Performed regression testing using BDD frameworks like Cucumber in Java, seamlessly integrating with the bank’s automation framework for comprehensive and efficient testing.}
      \resumeItem{Automated the creation of multiple JIRA tickets using Python scripts and Excel, achieving a 70\% reduction in task completion time and significantly enhancing team productivity.}
      \resumeItem{Volunteered to pack over 300 health kits for the homeless during Community Day.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Projects 1 -----------
\section{Projects}

\resumeSubHeadingListStart
  \resumeSubheading
    {Stock Market Prediction Using Genetic Programming}{April 2024}
    {Brock University}{}
    \resumeItemListStart
      \resumeItem{Developed a regression algorithm using genetic programming to predict NASDAQ and S\&P 500 prices, achieving up to 70\% accuracy.}
      \resumeItem{Conducted a comparative analysis of various stocks, researching procedures and algorithms, and synthesized findings into a comprehensive report.}
      \resumeItem{Learned the ECJ library and integrated it into the project, enhancing research capabilities with evolutionary computation techniques.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \resumeSubheading
    {AI Powered Web-Summarizer COSC-4P02 Software Engineering Project}{April 2023}
    {Brock University}{}
    \resumeItemListStart
    \resumeItem{Designed and implemented a full-stack Web-Summarizer tool using Java Spring Boot, Thymeleaf, and OpenAI to summarize web pages based on links or text, resulting in a robust solution for concise content summaries and sharing options.}
      \resumeItem{Served as Scrum Master and Developer, facilitating agile ceremonies and coordinating team efforts, resulting in timely project delivery and enhanced team productivity.}
      \resumeItem{Developed a comprehensive test plan covering all scenarios and conducted extensive regression testing, ensuring a high-quality product release with minimal defects.}
      \resumeItem{Implemented OAuth2 in the application, significantly enhancing security measures and protecting customer data.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \resumeSubheading
    {Village War Advanced OOPs Project}{April 2023}
    {Brock University}{}
    \resumeItemListStart
      \resumeItem{Designed a UML diagram for a complex game, utilizing object-oriented programming principles to create an efficient and comprehensive design.}
      \resumeItem{Developed game logic, rules, and user interaction mechanisms by integrating advanced Java OOP features, resulting in a top-tier implementation within the class.}
      \resumeItem{Incorporated the MVC design pattern in game development, enabling a graphical user interface and enhancing the game experience while improving scalability and maintainability.}
      \resumeItem{Revamped the project to utilize a multi-threaded client-server model with UDP protocol for packet sharing, resulting in notable enhancements in game performance.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Scholarships}
\resumeSubHeadingListStart

\resumeSubheading
  {Match of Minds Scholarship}{September 2024}
  {Brock University}{}
  \resumeItemListStart
    \resumeItem{Awarded a research scholarship based on faculty recommendations, selected as the sole recipient within the department.}
  \resumeItemListEnd

  \resumeSubheading
  {Dean's Honour List for Academic Year 3}{September 2024}
  {Brock University}{}
  \resumeItemListStart
    \resumeItem{Awarded to students maintaining an average above 80\%.}
  \resumeItemListEnd

\resumeSubheading
  {Golden Key Award}{January 2023}
  {Brock University}{}
  \resumeItemListStart
    \resumeItem{Recognized among the top 15\% of students in the faculty.}
  \resumeItemListEnd

  \resumeSubheading
  {Dean's Honour List for Academic Year 2}{January 2023}
  {Brock University}{}
  \resumeItemListStart
    \resumeItem{Awarded to students maintaining an average above 80\%.}
  \resumeItemListEnd

  \resumeSubheading
  {Dean's Honour List for Academic Year 1}{January 2022}
  {Brock University}{}
  \resumeItemListStart
    \resumeItem{Awarded to students maintaining an average above 80\%.}
  \resumeItemListEnd

\resumeSubheading
  {Brock Entrance Scholarship}{January 2021}
  {Brock University}{}
  \resumeItemListStart
    \resumeItem{Awarded to students with strong academic performance in senior secondary education.}
  \resumeItemListEnd

\resumeSubHeadingListEnd


\end{center}


\end{document}